Safe Transferable Regions

### 2015-11-16 paper/type-system.tex
Progress lemma.
Progress.
Preservation.
Preservation done.
Proofs proofs.
updates to section 3

\section{The Core Language}
\label{sec:type-system}

@@

We build on the Featherweight Generic Java (FGJ)~\cite{fgj} formalism
to formalize \name and its region type system. Our development reuses
notations from~\cite{fgj}, and relies on several of its definitions,
such as the definition of type well-formedness for the core
(region-free) language. We refrain from reproducing them here, and
instead encourage the reader to refer to~\cite{fgj,techrep}.

>>>>

\section{\fbname}
\label{sec:type-system}

In this section, we formally develop \fbname, a language that incorporates
the features introduced in the previous section, as well as its type system,
building on the Featherweight Generic Java (FGJ)~\cite{fgj} formalism.
Our development reuses notations and various definitions from~\cite{fgj},
such as the definition of type well-formedness for the core (region-free) language,
which are elaborated further in the supplement~\cite{techrep}.

@@
